---
title: "Getting started with binomial"
author: "Claudia Korea"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial 

The package `"binomial"` is an implementation for binomial functions relating to the binomial distribution

## Creating a binomial random variable

The first step is to create a `"binvar"` or a binomial variable with the function `bin_variable(trials, prob)`:

```{r}
myvar <- bin_variable(trials = 10, prob = 0.3)
```

`bin_variable(trials, prob)` takes two arguments, `trials` for how many trials occur and `prob` for the probability of a success.

You can print you `binvar` object to read the properties of the binary variable:
```{r}
print(myvar)
```

You can also print the summary of `binvar` object to find other properties of the binary random variable such as the mean, variance, mode, skewness and kurtosis:
```{r}
print(summary(myvar))
```

You can individually find the mean, variance, mode, skewness and kurtosis of a binomial distribution given the number of trials and the probability of success:
```{r}
#mean
bin_mean(trials = 10, prob = 0.3)

#variance
bin_variance(trials = 10, prob = 0.3)

#mode
bin_mode(trials = 10, prob = 0.3)

#skewness
bin_skewness(trials = 10, prob = 0.3)

#kurtosis
bin_kurtosis(trials = 10, prob = 0.3)

```


You can also use the function `bin_choose()` to find the number of combinations in which k successes can occur in n trials. Pass in the arguments `n` for n trials and `k` for k successes:
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 1:3)
```

You can find the probability of successes given the number of trials and the probability of success using the function `bin_probability()`. Pass in the arguments `successs` for the number of successes, `trials` for the number of trials and `prob` for the probability of success:
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
```

You can find the distribution of a binomial distribution using `bin_distribution()`. Pass in the arguments `trials` for the number of trials and `prob` for the probability of success and you will get an output of a data frame:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

You can also plot the distribution you find with the function `bin_distribution()`:
```{r}
plot(bin_distribution(trials = 5, prob = 0.5))
```

You can also find the cumulative probabilities of a binomial distribution using `bin_cumulative()`. Pass in the arguments `trials` for the number of trials and `prob` for the probability of success and you will get an output of a data frame with columns success for the number of successes, probability for the probability of the number of successes occuring, and then the column cumulative for the cumulative probability:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

You can also plot this cumulative probabilities table:
```{r}
plot(bin_cumulative(trials = 5, prob = 0.5))
```

